\newcommand{\lsd}[1] {\textit{#1}}
\section{Values relevants to initialize}
\begin{longtable}{||p{3cm}|p{10cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\end{longtable}

\section{Elements relevants to observe}
\begin{longtable}{||p{3cm}|p{10cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\end{longtable}

\section{List of all elements}
\subsection{Object \textbf{Root}}

Description: (no description available)


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\end{longtable}

\subsection{Object \textbf{Market}}

Description: 'Market' appears in the equation for: (Never Used).


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{LandPrice} &\textbf{Type: } Parameter
 
'LandPrice' appears in the equation for: ComputeValueNewMill, Decide. \\ \hline 
\lsd{LearningFactor} &\textbf{Type: } Parameter
 
'LearningFactor' appears in the equation for: ProductionKg. \\ \hline 
\lsd{PerceptionVar} &\textbf{Type: } Parameter
 
'PerceptionVar' appears in the equation for: PerceivedProdKg. \\ \hline 
\lsd{Price} &\textbf{Type: } Variable, 20 lags 
 
 'Price' appears in the equation for: CashFlow, ExpectedPrice. \\ \hline 
\lsd{RenovationCosts} &\textbf{Type: } Parameter
 
'RenovationCosts' appears in the equation for: ComputeValueNewMill, ComputeValueSC, Decide. \\ \hline 
\lsd{SCGrowth} &\textbf{Type: } Parameter
 
'SCGrowth' appears in the equation for: SCPotential. \\ \hline 
\lsd{SCReduction} &\textbf{Type: } Parameter
 
'SCReduction' appears in the equation for: SCProduction. \\ \hline 
\lsd{TotalProduction} &\textbf{Type: } Variable, 0 lags 
 
 Sum of the total production, zero NewCapacity and Renovation (for new iteration) and check market shares

'TotalProduction' appears in the equation for: PubKnowhow0, PubKnowhow1, Decide. \\ \hline 
\lsd{AvKgProductivityS} &\textbf{Type: } Variable, 0 lags 
 
 Calculate the average productivity of capital goods on supply

'AvKgProductivityS' appears in the equation for: MinimumProductivity. \\ \hline 
\lsd{AvSCPotential} &\textbf{Type: } Variable, 0 lags 
 
 Calculate the average SCPotential

'AvSCPotential' appears in the equation for: ComputeValueNewMill, Decide. \\ \hline 
\lsd{ComputeValueNewMill} &\textbf{Type: } Function, 0 lags 
 
Compute the scrapping value of buinding a new mill for the owner that called it

'ComputeValueNewMill' appears in the equation for: Decide. \\ \hline 
\lsd{ComputeValueKg} &\textbf{Type: } Function, 0 lags 
 
Compute the scrapping value of buying new capital good for the mill that called it. Should allways be called by a Mill

'ComputeValueKg' appears in the equation for: Decide. \\ \hline 
\lsd{ComputeValueSC} &\textbf{Type: } Function, 0 lags 
 
Compute the scrapping value of renovating the sugar cane area that called it. Should always be called by a SC

'ComputeValueSC' appears in the equation for: Decide. \\ \hline 
\lsd{ms0Sucrose} &\textbf{Type: } Parameter
 
'ms0Sucrose' appears in the equation for: TotalProduction, PubKnowhow0. \\ \hline 
\lsd{ms1Sucrose} &\textbf{Type: } Parameter
 
'ms1Sucrose' appears in the equation for: TotalProduction, PubKnowhow1. \\ \hline 
\lsd{ProductivityKgSBase} &\textbf{Type: } Variable, 0 lags 
 
 Basic growth of productivity of capital good available to new investment

'ProductivityKgSBase' appears in the equation for: ProductivityKgS. \\ \hline 
\lsd{AvKnowhow0} &\textbf{Type: } Parameter
 
'AvKnowhow0' appears in the equation for: TotalProduction, PubKnowhow0. \\ \hline 
\lsd{AvKnowhow1} &\textbf{Type: } Parameter
 
'AvKnowhow1' appears in the equation for: TotalProduction, PubKnowhow1. \\ \hline 
\lsd{PubKnowhow0} &\textbf{Type: } Variable, 1 lags 
 
 Public know-how for technology 0
Represents the spilling of private know-how into public know-how

'PubKnowhow0' appears in the equation for: PubKnowhow0, ComputeValueNewMill, Decide, SCExcess. \\ \hline 
\lsd{PubKnowhow1} &\textbf{Type: } Variable, 1 lags 
 
 Public know-how for technology 1
Represents the spilling of private know-how into public know-how

'PubKnowhow1' appears in the equation for: PubKnowhow1, ComputeValueNewMill, Decide, SCExcess, ProductionKg. \\ \hline 
\lsd{KnowhowLeak} &\textbf{Type: } Parameter
 
'KnowhowLeak' appears in the equation for: PubKnowhow0, PubKnowhow1. \\ \hline 
\lsd{CostFixMin} &\textbf{Type: } Parameter
 
'CostFixMin' appears in the equation for: Decide. \\ \hline 
\lsd{CostFixMax} &\textbf{Type: } Parameter
 
'CostFixMax' appears in the equation for: Decide. \\ \hline 
\lsd{CostVarAgricMin} &\textbf{Type: } Parameter
 
'CostVarAgricMin' appears in the equation for: Decide. \\ \hline 
\lsd{CostVarAgricMax} &\textbf{Type: } Parameter
 
'CostVarAgricMax' appears in the equation for: Decide. \\ \hline 
\lsd{ScrappingValue} &\textbf{Type: } Parameter
 
'ScrappingValue' appears in the equation for: Decide. 
 
 \textbf{Initial values:}  All 135 instances set to random values drawn from a uniform in the range [0.15,0.35]. \\ \hline 
\end{longtable}

\subsection{Object \textbf{Owner}}

Description: 'Owner' appears in the equation for: TotalProduction, AvSCPotential.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{CashOwner} &\textbf{Type: } Parameter
 
'CashOwner' appears in the equation for: CashFlow, Decide. 
 
 \textbf{Initial values:}  All 135 instances equal to 50000. \\ \hline 
\lsd{SCOwner} &\textbf{Type: } Variable, 0 lags 
 
 Sum the total production of sugar-cane under one owner

'SCOwner' appears in the equation for: (Never Used). \\ \hline 
\lsd{ProductionOwner} &\textbf{Type: } Variable, 0 lags 
 
 Sum of the production under the owner

'ProductionOwner' appears in the equation for: TotalProduction, CashFlow. \\ \hline 
\lsd{CashFlow} &\textbf{Type: } Variable, 0 lags 
 
 Manage cash flow
Production is sold, costs are paid and all revenue is centralized at the owner and investments are decided
Returns total income minus cost under the owner

'CashFlow' appears in the equation for: (Never Used). \\ \hline 
\lsd{ExpectedPrice} &\textbf{Type: } Variable, 0 lags 
 
 Price the owner expects to receive for production

'ExpectedPrice' appears in the equation for: ComputeValueNewMill, ComputeValueKg, ComputeValueSC, Decide. \\ \hline 
\lsd{Decide} &\textbf{Type: } Function, 0 lags 
 
Select the best investment option available and implement it. Return the kind of option chosen: 1 for sugar cane renovation, 2 for investment in existing mill (buy capital good), 3 for create new mill and -1 when no available options are good enough (scrapping value below minimum limit) or not affordable for the owner

'Decide' appears in the equation for: CashFlow. \\ \hline 
\lsd{TypeOwner} &\textbf{Type: } Variable, 0 lags 
 
 (no description available) \\ \hline 
\lsd{NumberMills} &\textbf{Type: } Variable, 0 lags 
 
 (no description available) \\ \hline 
\lsd{ms0SucroseOwner} &\textbf{Type: } Parameter
 
(no description available) \\ \hline 
\lsd{ms1SucroseOwner} &\textbf{Type: } Parameter
 
(no description available) \\ \hline 
\lsd{AvKnowhow0Owner} &\textbf{Type: } Parameter
 
(no description available) \\ \hline 
\lsd{AvKnowhow1Owner} &\textbf{Type: } Parameter
 
(no description available) \\ \hline 
\end{longtable}

\subsection{Object \textbf{Mill}}

Description: 'Mill' appears in the equation for: TotalProduction, AvSCPotential, CashFlow, Decide.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{Knowhow0} &\textbf{Type: } Parameter
 
'Knowhow0' appears in the equation for: TotalProduction, ComputeValueKg, Decide, SCExcess, PerceivedProdKg, ProductionKg. 
 
 \textbf{Initial values:}  All 4 instances equal to 0.6. \\ \hline 
\lsd{Knowhow1} &\textbf{Type: } Parameter
 
'Knowhow1' appears in the equation for: TotalProduction, ComputeValueKg, Decide, SCExcess, PerceivedProdKg, ProductionKg. 
 
 \textbf{Initial values:}  All 4 instances equal to 0.6. \\ \hline 
\lsd{NewCapacity} &\textbf{Type: } Parameter
 
'NewCapacity' appears in the equation for: TotalProduction, ComputeValueKg, Decide. \\ \hline 
\lsd{SCMill} &\textbf{Type: } Variable, 0 lags 
 
 Sum of all sugar-cane production under the mill

'SCMill' appears in the equation for: SCOwner, CashFlow, SCExcess, AvKgProductivity, ProductionKg. \\ \hline 
\lsd{MinimumProductivity} &\textbf{Type: } Variable, 0 lags 
 
 Minimum accepted productivity for a capital good to be used

'MinimumProductivity' appears in the equation for: SCExcess. \\ \hline 
\lsd{SCExcess} &\textbf{Type: } Variable, 0 lags 
 
 Amount of sugar-cane not processed
Is influenced by sugar-cane production and capacity of capital goods
Rank capital goods by productivity and supply them with sugar-cane imput (write SCImput). Control for disposal of old capital goods

'SCExcess' appears in the equation for: ComputeValueKg, ProductionMill. \\ \hline 
\lsd{ProductionMill} &\textbf{Type: } Variable, 0 lags 
 
 Summ of all capital goods productions under the mill

'ProductionMill' appears in the equation for: ProductionOwner, AvKgProductivity. \\ \hline 
\lsd{AvKgProductivity} &\textbf{Type: } Variable, 0 lags 
 
 Average productivity of all capital good under the mill
Is influenced by the productivity of capital goods

'AvKgProductivity' appears in the equation for: ComputeValueSC. \\ \hline 
\lsd{AvCostVarInd} &\textbf{Type: } Variable, 0 lags 
 
 Average variable cost of all capital good under the mill

'AvCostVarInd' appears in the equation for: ComputeValueSC. \\ \hline 
\lsd{CostFix} &\textbf{Type: } Parameter
 
'CostFix' appears in the equation for: CashFlow, Decide. 
 
 \textbf{Initial values:}  All 300 instances set to random values drawn from a uniform in the range [18900,22500]. \\ \hline 
\lsd{CostVarAgric} &\textbf{Type: } Parameter
 
'CostVarAgric' appears in the equation for: ComputeValueNewMill, ComputeValueKg, ComputeValueSC, CashFlow, Decide. 
 
 \textbf{Initial values:}  All 300 instances set to random values drawn from a uniform in the range [30,40]. \\ \hline 
\lsd{MinProdMult} &\textbf{Type: } Parameter
 
'MinProdMult' appears in the equation for: MinimumProductivity. 
 
 \textbf{Initial values:}  All 300 instances set to random values drawn from a uniform in the range [0.9,0.95]. \\ \hline 
\lsd{NewMill} &\textbf{Type: } Parameter
 
(no description available) 
 
 \textbf{Initial values:}  All 300 instances equal to 0. \\ \hline 
\lsd{TypeMill} &\textbf{Type: } Variable, 0 lags 
 
 (no description available) \\ \hline 
\end{longtable}

\subsection{Object \textbf{SC}}

Description: 'SC' appears in the equation for: TotalProduction, AvSCPotential, Decide.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{Renovation} &\textbf{Type: } Parameter
 
'Renovation' appears in the equation for: TotalProduction, Decide, SCProduction. \\ \hline 
\lsd{SCPotential} &\textbf{Type: } Variable, 1 lags 
 
 Potential production of sugar-cane of the mill
Is influenced by the area and by agricultural productivity
Grows exponetilly over time, representing agricultural productivity advances

'SCPotential' appears in the equation for: AvSCPotential, ComputeValueSC, Decide, SCPotential, SCProduction. 
 
 \textbf{Initial values:}  All 4 instances equal to 1500. \\ \hline 
\lsd{SCProduction} &\textbf{Type: } Variable, 1 lags 
 
 Actual production of sugar-cane of the mill
Is influenced by area, agricultural productivity, sugar-cane productivity loss over the harvests and by investiments in renovation
Falls over time. When renovation is made, increases to equal SCPotential

'SCProduction' appears in the equation for: ComputeValueSC, Decide, SCMill, SCProduction. 
 
 \textbf{Initial values:}  All 4 instances equal to 1500. \\ \hline 
\end{longtable}

\subsection{Object \textbf{Kg}}

Description: 'Kg' appears in the equation for: TotalProduction, CashFlow, Decide, SCExcess, AvCostVarInd.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{CapacityKg} &\textbf{Type: } Parameter
 
'CapacityKg' appears in the equation for: Decide, SCExcess, ProductionKg. \\ \hline 
\lsd{ProductivityKg} &\textbf{Type: } Parameter
 
'ProductivityKg' appears in the equation for: Decide, SCExcess, PerceivedProdKg, ProductionKg. \\ \hline 
\lsd{SCImput} &\textbf{Type: } Parameter
 
'SCImput' appears in the equation for: Decide, SCExcess, ProductionKg. \\ \hline 
\lsd{TypeKg} &\textbf{Type: } Parameter
 
'TypeKg' appears in the equation for: TotalProduction, Decide, PerceivedProdKg, ProductionKg. \\ \hline 
\lsd{PerceivedProdKg} &\textbf{Type: } Variable, 0 lags 
 
 Productivity of the capital good as perceived by the owner
Is influenced by the actual productivity of the capital good, the know-how in the mill and some mistake in perception

'PerceivedProdKg' appears in the equation for: SCExcess. \\ \hline 
\lsd{ProductionKg} &\textbf{Type: } Variable, 0 lags 
 
 Sacarose extracted from sugar-cane
Is influenced by productivity, know-how and imput
First, it absorbs public know-how
After production, proportional to usage, increases know-how for its type

'ProductionKg' appears in the equation for: TotalProduction, CashFlow, ProductionMill. \\ \hline 
\lsd{CostVarInd} &\textbf{Type: } Parameter
 
'CostVarInd' appears in the equation for: CashFlow, Decide, AvCostVarInd. 
 
 \textbf{Initial values:}  All 4 instances equal to 0.05. \\ \hline 
\end{longtable}

\subsection{Object \textbf{KSupplier}}

Description: 'KSupplier' appears in the equation for: AvKgProductivityS, ComputeValueNewMill, ComputeValueKg.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{ProdGrowth} &\textbf{Type: } Parameter
 
'ProdGrowth' appears in the equation for: ProductivityKgSBase. \\ \hline 
\end{longtable}

\subsection{Object \textbf{Technology}}

Description: 'Technology' appears in the equation for: AvKgProductivityS, ComputeValueNewMill, ComputeValueKg.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{CapacityKgS} &\textbf{Type: } Parameter
 
'CapacityKgS' appears in the equation for: ComputeValueNewMill, ComputeValueKg, Decide. \\ \hline 
\lsd{PriceKgS} &\textbf{Type: } Parameter
 
'PriceKgS' appears in the equation for: ComputeValueNewMill, ComputeValueKg, Decide. \\ \hline 
\lsd{TypeKgS} &\textbf{Type: } Parameter
 
'TypeKgS' appears in the equation for: ComputeValueNewMill, ComputeValueKg, Decide. \\ \hline 
\lsd{ProductivityKgS} &\textbf{Type: } Variable, 1 lags 
 
 Productivity of capital good available to new investment
Grows over time according to ProductivityKgSBase

'ProductivityKgS' appears in the equation for: AvKgProductivityS, ComputeValueNewMill, ComputeValueKg, Decide, ProductivityKgS. \\ \hline 
\lsd{CostVarIndS} &\textbf{Type: } Parameter
 
'CostVarIndS' appears in the equation for: ComputeValueNewMill, ComputeValueKg, Decide. 
 
 \textbf{Initial values:}  All 4 instances equal to 0.05. \\ \hline 
\end{longtable}

